### 2015-05-07 papers/histogram/thesis/thesis.tex
fix build issue in histogram/thesis Tested on bennet. Took 0:27.63.

\begin{figure}[H]
  \centering
  \includegraphics[width=0.75\textwidth]
  {figs/internal-energy-comps.pdf}
  \caption[Internal energy error comparisons]
  {Internal energy error comparisons}
  \label{fig:u_comps}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.75\textwidth]
  {figs/heat-capacity-comps.pdf}
  \caption[Heat capacity error comparisons]
  {Heat capacity error comparisons}
  \label{fig:u_comps}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.75\textwidth]
  {figs/config-entropy-comps.pdf}
  \caption[Configurational entropy error comparisons]
  {Configurational entropy error comparisons}
  \label{fig:u_comps}
\end{figure}

>>>>

\begin{figure}[H]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/internal-energy-comps.pdf}
  \caption[Internal energy error comparisons]
  {Internal energy error comparisons}
  \label{fig:u_comps}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/heat-capacity-comps.pdf}
  \caption[Heat capacity error comparisons]
  {Heat capacity error comparisons}
  \label{fig:u_comps}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/config-entropy-comps.pdf}
  \caption[Configurational entropy error comparisons]
  {Configurational entropy error comparisons}
  \label{fig:u_comps}
\end{figure}
